Fast and optimal centroiding of faint stars

### 2015-02-15 ms/figure.tex
Update figure.tex

\begin{abstract}
One of the most demanding tasks in astronomical image processing---in terms of precision---is
the centroiding of stars. Upcoming large surveys are going to take images of billions of point sources, 
including many faint stars, with short exposure times. Real-time estimation of the
centroid of stars is crucial for real-time PSF estimation, and precision is required
for measurements of proper motion. In this work, we aim to compare the performance of
fast and slow centroiding methods, when they are applied
to relatively low signal-to-noise ratio stars in a wide range of psf sizes.
In order to investigate how information-preserving these techniques are, we compare
the root-mean-squared-error arising from these centroiding methods with the fundamental Cramer-Rao
lower bound.

>>>>

\begin{abstract}
One of the most demanding tasks in astronomical image processing---in terms of precision---is the centroiding of stars. 
Upcoming large surveys are going to take images of billions of point sources, 
including many faint stars, with short exposure times. Real-time estimation of the
centroid of stars is crucial for real-time PSF estimation, and precision is required
for measurements of proper motion. In this work, we aim to compare the performance of
fast and slow centroiding methods, when they are applied
to relatively low signal-to-noise ratio stars in a wide range of psf sizes.
In order to investigate how information-preserving these techniques are, we compare
the root-mean-squared-error arising from these centroiding methods with the fundamental Cramer-Rao
lower bound. We discuss two general circumstances in centroiding of faint stars: (i) when we have a good estimate
of the PSF, (ii) when we do not know the PSF. In the case that we know the PSF, we show that a fast
 polynomial centroiding after smoothing the image by the PSF can be 
as accurate as PSF profile fitting with a good PSF estimate. In the case that we do not
know the PSF, we demonstrate that although a particular form of polynomial centroiding method is not as
accurate as PSF profile fitting, it comes close to saturating the Cramer-Rao lower bound
in a wide range of conditions.
